`r spec$datasetname`

### 2025-03-20 report/CONJ_COMD.qmd
update template

```{r}
#| include: false
#| cache: false
library(publishTC)
library(ggplot2)
library(patchwork)
library(plotly)
spec <- yaml::read_yaml(params$file)
spec_series <- spec$series
list_files <- list.files(pattern = "csv$", path = file.path(dirname(params$file), spec$dataset), full.names = TRUE, include.dirs = FALSE)
all_data <- lapply(list_files, read.ts, list = TRUE)
names(all_data) <- tools::file_path_sans_ext(basename(list_files))
n <- length(all_data)
if (n == 1) {
    spec$plots$revision_history$enabled <- FALSE
}
series <- names(all_data[[1]])
names(series) <- series

@@

if (spec$plots$extra_info$enabled) {
	extra_info <- lapply(last_est, function(sect) {
		res <- lapply(sect, summary)
		res <- do.call(
			rbind,
			lapply(res, function(x){
				x[["I/C ratios"]] <- NULL
				unlist(x)
			}))
		rownames(res) <- gsub("\n", " ", rownames(res))
		res
	})

	if (length(grep("robust", studied_methods)) > 0) {
		outliers <- lapply(spec_series, `[[`, "outliers")
	} else {
		outliers <- lapply(spec_series, function(x) NULL)
	}

if (spec$plots$revision_history$enabled) {
	rev_to_table <- function(x) {
		data_rev <- t(do.call(ts.union, x))
		data_rev <- data_rev[,ncol(data_rev):1] # last date first
		data_rev <- data.frame(
			`Last date` = gsub("_", "-", rep(colnames(x[[1]]), length(x))),
			Methods = rep(names(x), each = ncol(x[[1]])), 
			data_rev,
			check.names = FALSE)
		colnames(data_rev)[-(1:2)] <- rev(format(zoo::as.Date(time(x[[1]])), "%Y-%m"))
		rownames(data_rev) <- NULL
		data_rev
	}
	dt_table <- function(data, group_cols = 2, i_row_name = 1, nb_digits = digits,
						 caption = NULL) {
		group_cols[group_cols > i_row_name] <- group_cols[group_cols > i_row_name] - 1
		is_num <- which(sapply(data[,-i_row_name], is.numeric))
		DT::datatable(
			data[,-i_row_name],
			extensions = c("RowGroup", "Buttons"),
			options = list(
				rowGroup = list(dataSrc = group_cols),
				columnDefs = list(list(targets = group_cols, visible = FALSE)),
				dom = "Brtipl",
				buttons = c("copy", "csv", "excel", "pdf")
			),
			selection = "none",
			rownames = data[,i_row_name],
			caption = caption
		) |>  DT::formatRound(columns = is_num,
							  digits= nb_digits)
	}

	rev_data <- lapply(basename(list_files), function(f){
		res <- lapply(studied_methods, function(method) {
			read.ts(file.path(dirname(params$file), spec$dataset, method, f), list = TRUE)
		})
		c(list("Raw data" = lapply(all_data[[tools::file_path_sans_ext(f)]], window, 
								   start = min(sapply(spec_series, `[[`, "first_date")))),
		  res)
	})
	names(rev_data) <- names(all_data)
	rev_data <- rev(rev_data)
	rev_data_ <- lapply(names(rev_data[[1]][[1]]), function(serie){
		res <- lapply(names(rev_data[[1]]), function(method){
			do.call(ts.union, lapply(rev_data, function(x){
				x[[method]][[serie]]
			}))
		})
		names(res) <- names(rev_data[[1]])
		res
	})
	names(rev_data_) <- names(rev_data[[1]][[1]])
	rev_data <- rev_data_
	rm(rev_data_)

	if (spec$plots$revision_history$table$contribution_of_sa) {
		rev_data_fixed <- lapply(series, function(serie) {
			spec_s <- spec$series[[serie]]
			y <- window(all_data[[n]][[serie]], start = spec$series[[serie]]$first_date)
			vintages <- lapply(all_data[-n], function(vintage){
				window(y, end = end(vintage[[serie]]))
			})
			lapply(studied_methods, function(method) {
				method_name <- names(studied_methods)[which(studied_methods == method)]
				res <- c(lapply(vintages, function(x) {

		rev_tot <- lapply(series, function(serie) {
			rev_by_method <- lapply(names(studied_methods), function(method){
				data <- rev_data_fixed[[serie]][[method]]
				data_tot <- rev_data[[serie]][[method]]
				rev_tc <- (data[,1] - data)
				rev_tot <- (data_tot[,1] - data_tot)
				rev_tot <- rev_tot
				rev_sa <- rev_tot - rev_tc
				colnames(rev_tc) <- colnames(rev_sa) <- colnames(rev_tot) <- colnames(data_tot)
				list(
					Total = rev_tot, 
					`Due to revisions on SA` = rev_sa, 
					`Due to update of TC model` = rev_tc
				)
			})
			names(rev_by_method) <- names(studied_methods)
			rev_tot_by_method <- do.call(
				rbind,
				lapply(names(rev_by_method), function(method){
					rev_meth <- rev_to_table(rev_by_method[[method]])
					cbind(Meth = method, rev_meth)
				})
			)
			rev_tot_by_method <- rev_tot_by_method[rev_tot_by_method[, "Last date"] != colnames(rev_tot_by_method)[4], -4]
			rev_tot_by_method[with(rev_tot_by_method, order(Meth,`Last date`, Methods)), ]
		})
	}

@@

>>>>

```{r}
#| include: false
#| cache: false
library(publishTC)
library(ggplot2)
library(patchwork)
library(plotly)
spec <- yaml::read_yaml(params$file)
spec_series <- spec$series
series <- names(spec_series)
names(series) <- series
list_files <- list.files(pattern = "csv$", path = file.path(dirname(params$file), spec$dataset), full.names = TRUE, include.dirs = FALSE)
all_data <- lapply(list_files, read.ts, list = TRUE)
names(all_data) <- tools::file_path_sans_ext(basename(list_files))
all_data <- lapply(all_data, `[`, series)
n <- length(all_data)
if (n == 1) {
    spec$plots$revision_history$enabled <- FALSE
}

@@

@@

```{r}
#| label: extra-info
#| eval: !expr spec$plots$extra_info$enabled
extra_info <- lapply(last_est, function(sect) {
    res <- lapply(sect, summary)
    res <- do.call(
        rbind,
        lapply(res, function(x){
            x[["I/C ratios"]] <- NULL
            unlist(x)
        }))
    rownames(res) <- gsub("\n", " ", rownames(res))
    res
})

if (length(grep("robust", studied_methods)) > 0) {
    outliers <- lapply(spec_series, `[[`, "outliers")
} else {
    outliers <- lapply(spec_series, function(x) NULL)
}
```

```{r}
#| label: revision-history
#| eval: !expr spec$plots$revision_history$enabled
rev_to_table <- function(x) {
    data_rev <- t(do.call(ts.union, x))
    data_rev <- data_rev[,ncol(data_rev):1] # last date first
    data_rev <- data.frame(
        `Last date` = gsub("_", "-", rep(colnames(x[[1]]), length(x))),
        Methods = rep(names(x), each = ncol(x[[1]])), 
        data_rev,
        check.names = FALSE)
    colnames(data_rev)[-(1:2)] <- rev(format(zoo::as.Date(time(x[[1]])), "%Y-%m"))
    rownames(data_rev) <- NULL
    data_rev
}
dt_table <- function(data, group_cols = 2, i_row_name = 1, nb_digits = digits,
                     caption = NULL) {
    group_cols[group_cols > i_row_name] <- group_cols[group_cols > i_row_name] - 1
    is_num <- which(sapply(data[,-i_row_name], is.numeric))
    DT::datatable(
        data[,-i_row_name],
        extensions = c("RowGroup", "Buttons"),
        options = list(
            rowGroup = list(dataSrc = group_cols),
            columnDefs = list(list(targets = group_cols, visible = FALSE)),
            dom = "Brtipl",
            buttons = c("copy", "csv", "excel", "pdf")
        ),
        selection = "none",
        rownames = data[,i_row_name],
        caption = caption
    ) |>  DT::formatRound(columns = is_num,
                          digits= nb_digits)
}

rev_data <- lapply(basename(list_files), function(f){
    res <- lapply(studied_methods, function(method) {
        read.ts(file.path(dirname(params$file), spec$dataset, method, f), list = TRUE)[series]
    })
    c(list("Raw data" = lapply(all_data[[tools::file_path_sans_ext(f)]], window, 
                               start = min(sapply(spec_series, `[[`, "first_date")))),
      res)
})
names(rev_data) <- names(all_data)
rev_data <- rev(rev_data)
rev_data_ <- lapply(names(rev_data[[1]][[1]]), function(serie){
    res <- lapply(names(rev_data[[1]]), function(method){
        do.call(ts.union, lapply(rev_data, function(x){
            x[[method]][[serie]]
        }))
    })
    names(res) <- names(rev_data[[1]])
    res
})
names(rev_data_) <- names(rev_data[[1]][[1]])
rev_data <- rev_data_
rm(rev_data_)
```

```{r}
#| label: revision-history-contribution-sa
#| eval: !expr spec$plots$revision_history$enabled & spec$plots$revision_history$table$contribution_of_sa
rev_data_fixed <- lapply(series, function(serie) {
    spec_s <- spec$series[[serie]]
    y <- window(all_data[[n]][[serie]], start = spec$series[[serie]]$first_date)
    vintages <- lapply(all_data[-n], function(vintage){
        window(y, end = end(vintage[[serie]]))
    })
    lapply(studied_methods, function(method) {
        method_name <- names(studied_methods)[which(studied_methods == method)]
        res <- c(lapply(vintages, function(x) {

rev_tot <- lapply(series, function(serie) {
    rev_by_method <- lapply(names(studied_methods), function(method){
        data <- rev_data_fixed[[serie]][[method]]
        data_tot <- rev_data[[serie]][[method]]
        rev_tc <- (data[,1] - data)
        rev_tot <- (data_tot[,1] - data_tot)
        rev_tot <- rev_tot
        rev_sa <- rev_tot - rev_tc
        colnames(rev_tc) <- colnames(rev_sa) <- colnames(rev_tot) <- colnames(data_tot)
        list(
            Total = rev_tot, 
            `Due to revisions on SA` = rev_sa, 
            `Due to update of TC model` = rev_tc
        )
    })
    names(rev_by_method) <- names(studied_methods)
    rev_tot_by_method <- do.call(
        rbind,
        lapply(names(rev_by_method), function(method){
            rev_meth <- rev_to_table(rev_by_method[[method]])
            cbind(Meth = method, rev_meth)
        })
    )
    rev_tot_by_method <- rev_tot_by_method[rev_tot_by_method[, "Last date"] != colnames(rev_tot_by_method)[4], -4]
    rev_tot_by_method[with(rev_tot_by_method, order(Meth,`Last date`, Methods)), ]
})
```
